\documentclass[12pt,lineno]{gsajnl}
% \documentclass[9pt,twocolumn,twoside]{gsajnl}
% Use the documentclass option 'lineno' to view line numbers

\articletype{inv} % article type
% {inv} Investigation 
% {gs} Genomic Selection
% {goi} Genetics of Immunity 
% {gos} Genetics of Sex 
% {mp} Multiparental Populations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Package
\usepackage{amssymb}
\usepackage{verbatim}
%\usepackage[francais,english]{babel}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{lineno}
%\usepackage[latin1]{inputenc}
%\usepackage[table]{xcolor}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Define
\definecolor{light-gray}{gray}{0.8}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Setup
\title{Fast inference of individual admixture coefficients using geographic data}

% \author{Kevin Caye$^1$, Flora Jay$^2$, Olivier Michel$^3$, Olivier Fran\c cois$^1$}
\author[$\ast$,1]{Author One}
\author[$\dagger$]{Author Two}
\author[$\ddagger$]{Author Three}
\author[$\S$]{Author Four}
\author[$\ast\ast$]{Author Five}

\affil[$\ast$]{Author one affiliation}
\affil[$\dagger$]{Author two affiliation}
\affil[$\ddagger$]{Author three affiliation}
\affil[$\S$]{Author four affiliation}
\affil[$\ast\ast$]{Author five affiliation}

\keywords{Ancestry Estimation Algorithms; Genotypic Data; Geographic Data; Fast Algorithms}

\runningtitle{GENETICS Journal Template on Overleaf} % For use in the footer 

\correspondingauthor{Corresponding Author}

\begin{abstract}
Accurately evaluating the distribution of genetic ancestry across geographic space is one of the main questions addressed by evolutionary biologists. This question has been commonly addressed through the application of Bayesian estimation programs allowing their users to estimate individual admixture proportions and allele frequencies among putative ancestral populations. Following the explosion of high-throughput sequencing technologies, several algorithms have been proposed to cope with computational burden generated by the massive data in those studies. In this context, incorporating geographic proximity in ancestry estimation algorithms is an open statistical and computational challenge. In this study, we introduce new algorithms that use geographic information to estimate ancestry proportions and ancestral genotype frequencies using population genetic data. Our algorithms combine matrix factorization methods and spatial statistics to provide estimates of ancestry matrices based on least-squares approximation.  We demonstrate the benefit of using spatial algorithms through extensive computer simulations, and we provide an example of application of our new algorithms to a set of spatially referenced samples for the plant species {\it Arabidopsis thaliana}.  Without lost of statistical accuracy, the new algorithms exhibit runtimes that are much shorter than those observed for previously developed spatial methods. Our algorithms are implemented in the {\tt R} package, {\tt tess3r}, which is available from public repositories. 
\end{abstract}

\setboolean{displaycopyright}{true}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document
\begin{document}
\baselineskip 0.8cm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Setup
\maketitle
\thispagestyle{firststyle}
\marginmark
\firstpagefootnote
\correspondingauthoraffiliation{
$^1$ Universit\'e Grenoble-Alpes, Centre National de la Recherche Scientifique, TIMC-IMAG UMR 5525, 38042 Grenoble, France.\\
$^2$ Universit\'e de Flora.
$^3$ Universit\'e Grenoble-Alpes, Centre National de la Recherche Scientifique, Gipsa-lab UMR 5216, 38042 Grenoble, France.
}
\vspace{-11pt}%

\input{intro.tex}
\input{method.tex}
\input{results.tex}
\input{discussion.tex}

\section*{Acknowledgments} 

This work has been partially supported by the LabEx PERSYVAL-Lab (ANR-11-LABX-0025-01) funded by the French program Investissement d\rq{}Avenir. Olivier Fran\c cois acknowledges support from Grenoble INP and from the Agence Nationale de la Recherche, project AFRICROP ANR-13-BSV7-0017.

\newpage 

\input{references.tex}
\input{tables_figures.tex}


\end{document}

    
